City traffic, IoT and Blockchain technologies

### 2020-10-20 thesis/report2.tex
One more section completed on report 2.

\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

@@

    The global format of such a JSON needs the ability to transport any type of message. Therefore the listing \ref{lst:jsonEnvelope} represents such a message.

>>>>

\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{dirtytalk}

@@

    The global format of such a JSON has the ability to transport any type of message. Therefore the listing \ref{lst:jsonEnvelope} represents such a message. The envelope, on its turn, contains another message, of different formats. Listing \ref{lst:jsonClientEnums} shows one example of such a contained message. It is the way a client reports one line it is travelling onto or one line it has just finished travelling. Both listings, \ref{lst:jsonEnvelope} and \ref{lst:jsonClientEnums}, show json schema messages.

    Another aspect of those messages is that an actor can send a message of type \textit{AskForLine} and afterwards it is expecting a message back with details about that line (e.g. how many other actors are travelling on it). The question of uttermost importance is: to whom does it send this message? In \cite{MicroservicesCityTrafficSimulation} the authors use a \textit{central server} and each actor is communicating only with it. However, having already set a foot into the world of decentralized systems, we do not have anymore a \textit{central server}. A decentralized ledger or blockchain or system, soon to be discussed in \ref{sec:EthereumNature}, has no such concept of \textit{server}. For the moment of this paragraph which is concerned only with the way an actor is communicating, we can assume that there are two components: the \textit{frontend} one and the \textit{backend} one. The \textit{frontend} one is concerned with showing information to the user (graphical, text, etc.) and also computing (via classic algorithms or Artifical Intelligence algorithms) the things which a user needs (e.g. shortest or fastest path from one point to another). To obtain various benefits along those computations there are certain types of information which have to be obtained. There is static information like the map of the city where the actor is in and there is dynamic information about what is currently, at the time of the computation or at the certain and precisely known time in the future, happening in the city. One reiterated example is how many actors are already on a certain line in the city. Having this information for the lines which would represent one of the paths the querying actor can run onto, the computations can compute more accurately a shorter (time wise) path or it can optimize various other outcomes. So far this has been the \textit{frontend}. The other part is the \textit{backend}. This is concerned less with how the data is presented to the user and how the computations are working. Its concerns are how to obtain the data needed by the \textit{frontend} and how to serve it. Thus it can be a server where all the actors are calling into. But it also can be one of the peers which are part of a decentralized network like Ethereum or IOTA. It can take care of all the nitty-gritty parts. It can compile various types of data, it can run necessary validations which are mandatory in such types of networks and so on. More details about how it does this are not part of this paragraph or of this chapter but they will be discussed later on on this thesis. Such distinctions between \textit{frontend} and \textit{backend} can also been seen in \cite{ApproachesToFrontEnd} where, among few options, there are standalone nodes responsible for participating into the network and a \say{local device} which offers \say{local} functionalities for various applications.
